\documentclass[letterpaper,10pt]{article}
\usepackage{amsmath, amsthm, amssymb}

%\usepackage[
%ps2pdf,                %%% hyper-references for ps2pdf
%bookmarks=true,%                   %%% generate bookmarks ...
%bookmarksnumbered=true,%           %%% ... with numbers
%hypertexnames=false,%              %%% needed for correct links to figures !!!
%breaklinks=true,%                  %%% breaks lines, but links are very small
%linkbordercolor={0 0 1}
%]{hyperref}%  %%% border-width of frames 

%-----------------------------------------------------------
%Margin setup
\usepackage[breaklinks=false]{hyperref} 

\setlength{\voffset}{0.0in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{12in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.3in}
\setlength{\evensidemargin}{-0.7in}

%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
\usepackage{eurosym}
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

% From website http://www.cse.wustl.edu/~mgeorg/html/tildalatex.html
\def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
\def\urldot{\kern -.10em.\kern -.10em}
\def\urlhttp{http\kern -.10em\lower -.1ex\hbox{:}\kern -.12em\lower 0ex\hbox{/}\kern -.18em\lower 0ex\hbox{/}}


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Shaoting Zhang} & {Gender: female} \\
  8000 U.S. 290 West Apt. 10407 &  {\tt sxz152930@utdallas\urldot edu} \\
Austin, TX 78736 & {Mobile: (737)-529-7160} \\
\end{tabular*}
\\

%\vspace{-2mm}

%\parindent=0.8cm \resheading{~Profile}
%    \vspace{-4mm}
%%    \parindent=1cm {Seasoned EDA professional with 8 years of industry experience in algorithm development, implementation, and deployment of high quality CAD tools.  Brings solid design knowledge due to close collaboration with microprocessor design teams.  Strong research experience in physical design and circuit reliability.  Good team player with experience in leading multiple people team to achieve targets on time.}
%    \parindent=1cm {Seasoned EDA software engineer with 8 years of industry experience in algorithm development, implementation, and deployment of high quality software tools.  Expertise includes optimization algorithms and graph theory with solid implementation in C++/STL.  Good team player with experience in leading multiple people team to achieve targets on time.}
%\vspace{-3mm}

{
\vspace{-5mm}
\center
\resheading{Seek Intern/Fulltime Hardware Engineering Position starting at Fall 2017}
\vspace{-10mm}
}

\resheading{Education}
\begin{itemize}
    \vspace{-7mm}
\item
    \ressubheading{University of Texas at Dallas}{Dallas, TX}{Master Student, Department of ECE} {Aug. 2015 -- Dec. 2017 (Expected)}
	      \begin{itemize}
	          \resitem{GPA: 11.4/12} 
            \resitem {Relevant Courses: {VLSI Design}, {Advanced Digital Logic}, {Computer Architecture (A)}, {Design and Analysis of Computer Algorithms (A)}, {Dynamics Of Complex Networks and Systems (A)}, {Analog Integrated Circuit Design}, {Power Management Circuits}, {Digital Signal Processing}, {Linear Systems (A)}, {Energy Harvesting, Storage and Powering for Microsystems}}
	      \end{itemize}


\item
    \ressubheading{{Nanjing University of Post and Telecommunications}}	{Nanjing, China}{Bachelor of Engineering, Department of Communication Engineering}			{Sep. 2009 -- Jul. 2013}
        \begin{itemize}
            \resitem {Relevant Courses: {Principles of Communications}, {Signals and Systems}, {Principles of Digital \& Analog Integrated Circuits}, {Random Signals and Statistics}, {Discrete Structures}}
        \end{itemize}

\end{itemize} % End Education list

\vspace{-3mm}
%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}

\begin{itemize}
    \vspace{-7mm}

\item
    \ressubheading{{China Electronics Technology Group Corporation}}{Nanjing, China}{Silicon Testing Engineer}{Jul. 2013 -- Jul. 2014}
             { %\small
        \begin{itemize}
            \resitem {Wafer level testing before IC packaging}
            \resitem {Quality testing of power tube inside the gold bonding for silicon BJT (Bipolar Junction Transistor) and LDMOS (Laterally Diffused Metal Oxide Semiconductor). Parameter testing and performance evaluations on output power and power gain fluctuations of BJT and LDMOS}	
        \end{itemize}
                }

\end{itemize}

\vspace{-4mm}
\resheading{Course Projects}
\begin{itemize}
\vspace{-7mm}


\item { {\bf Advanced Digital Logic:}}
 \vspace{-1mm}
        \begin{itemize}
            %\resitem { {Pump Controller:} Design in Moore machine, Mealy machine and asynchronous circuits. Power, performance and area (PPA) trade-off analysis with Synopsys Design Vision}
            \resitem { Pump controller design and power, performance, area (PPA) trade-off with Synopsys Design Vision}
            \resitem { Logic synthesis from VHDL to gate-level netlist using Synopsys Design Vision. Fault detection with automatic test pattern generation and logic simulation}
        \end{itemize}
  \vspace{-1mm}

\item { {\bf VLSI Design:} The Trivium Stream Cipher} 
 \vspace{-1mm}
	\begin{itemize}
            %\resitem {Schematic and layout designs for the inverter, 2-input NAND gate, 2-input NOR gate and Flip-Flop in Cadence. Show the energy, power, area and delay using Synopsys HSPICE}
		\resitem {Implement the Trivium stream cipher with inverters, NAND gates, NOR gates and Flip-Flops. Functional simulation and testing in schematic and layout}
	\end{itemize}
  \vspace{-1mm}

%\item { {\bf Analog IC Design:} A High-Gain, High-Speed Operational Amplifier}
% \vspace{-1mm}
%        \begin{itemize}
%           \resitem {Design a fast-settling op-amp for a switched-capacitor pipeline analog-to-digital converter (ADC)}
%			     \resitem {Design a folded cascode single-stage topology under settling time constraint with Cadence Virtuoso and Synopsys HSPICE}
%		    \end{itemize}
%\vspace{-1mm}



\item { {\bf Computer Architecture:} Cache Simulation and Optimization}
 \vspace{-1mm}
	    \begin{itemize}
		      \resitem {Cache performance evaluations varying capacities, associativities and block sizes using SimpleScalar}
		      \resitem {Instruction set optimization with parallelism and pipelining techniques. Adopt a SIMD instruction to unfold the ``for" loop. Achieve 26\% improvement on the instruction cache miss rate compared with the original C programs with MediaBench test cases}
	    \end{itemize}
 \vspace{-1mm}



\item { {\bf Algorithms: Design and Analysis:} Algorithm Analysis and Implementations}
 \vspace{-1mm}
	    \begin{itemize}
		      \resitem { Python implementations of sorting and graph algorithms, such as QuickSort, MergeSort, Dijkstra's algorithm, Karger's algorithm and computing strongly connected components}
	    \end{itemize}
  \vspace{-1mm}

\item { {\bf Dynamics Of Complex Networks and Systems:} The Network Modeling for Game Of Thrones}
 \vspace{-1mm}
	    \begin{itemize}
        	\resitem {Python implementation of the weighted graph for the social network in Game of Thrones}
		      \resitem {Describe and analyze the social network properties like the centrality, diameter and power law}
	    \end{itemize}
  \vspace{-1mm}

\end{itemize}

  
  \vspace{-4mm}
\resheading{Skills}
\begin{description}
    \vspace{-7mm}
\item[Languages/Scripting:] Python, C language, SPICE/HDL
   \vspace{-1mm}
\item[Applications:] Cadence Virtuoso/Schematic, Synopsys Design Vision, Matlab
%\item[Applications:] Unix System, Microsoft Office, Matlab
\vspace{-1mm}
\item[Miscellaneous:] Self-motivated, good communication and team-work skills.
\end{description}

\vspace{-4mm}
\resheading{Immigration Status: F-1 Student Visa (no need for H1B sponsorship)}

\end{document}
